\noindent \textit{\textcolor{red!60!black}{
The authors made no comment about the fact that the 1933 and 1934 coefficients do not seem statistically different than the 1930 effects (Figure 3).
}}

\bigskip

\noindent We acknowledge this observation, and we now address it in the revised manuscript. Two points bear on it. First, the identifying contrast in our design is not between the litigation years and 1930, but between each litigation year and the omitted base year of 1932---the year immediately preceding the abrogation. Relative to 1932, the 1933 and 1934 interaction coefficients are individually significant, whereas none of the pre-treatment coefficients, including 1930, is. The relevant difference-in-differences comparison therefore holds; requiring 1933 to be statistically distinguishable from a separately and noisily estimated 1930 coefficient is not the contrast that identifies the effect. Second, the confidence intervals around individual year estimates are wide given two-way clustered standard errors in a sample of this size, so pairwise comparisons between any two individual years will often fail to reach significance.

\medskip
\noindent The relevant question for parallel trends is not whether each pre-treatment year can be individually distinguished from 1933 or 1934, but whether the pre-treatment coefficients display individually significant departures from zero or a systematic trend leading into the treatment period. Neither is present. The pre-treatment coefficients in column 2 of Table 4 are $+0.026$, $+0.012$, $+0.022$, $-0.032$, and $-0.007$ for 1927 through 1931, respectively, none of which is statistically significant. Crucially, these coefficients are uniformly small and individually insignificant, and the two years immediately preceding the litigation---1931 ($-0.007$) and the omitted 1932 ($0.000$)---sit essentially at zero, so there is no trend running into the treatment window that could account for the sharp 1933 effect.

\medskip
\noindent The 1930 dip ($-0.032$, insignificant) deserves a brief comment. In 1930 the Great Depression was already deepening---bank failures were accelerating and credit conditions were tightening sharply. Since gold-exposed firms were systematically more leveraged (Table 2), they may have been somewhat more sensitive to this general credit contraction than unexposed firms, independent of gold clause exposure. The fact that this coefficient is small and insignificant, and is followed by coefficients of $-0.007$ and $0.000$ (omitted) in 1931--1932, is more consistent with occasional noise than with a persistent pre-trend.

\medskip
\noindent That said, we acknowledge that limited statistical power prevents us from rejecting the null that the 1930 coefficient equals the 1933 or 1934 coefficient. We have added a sentence to Section 5 noting that the parallel trends argument rests on the full pre-treatment pattern rather than year-by-year pairwise tests, and that the absence of a visible trend in the point estimates provides the primary support for this assumption.
