\noindent \textit{\textcolor{red!60!black}{
One small comment---my understanding (though I could be wrong) is that repurchases in the open market were not allowed post 1929. I imagine the main reason driving the decline in shares was reorganizations. If that is the case, it is not obvious one would want to include this if the point of the analysis is to estimate whether firms were using payout policy to preemptively give the cash to shareholders. That said, the results in Table 4 show that the effects are driven by dividends, not repurchases, so this is mostly about guiding modern readers on what firm policies were in the 1930s.
}}

\bigskip

\noindent The referee is essentially correct. Open-market repurchases as a deliberate payout vehicle were essentially absent among industrial firms in this period. The Securities Exchange Act of 1934 had only just established the SEC, and firms faced substantial risk that market purchases of their own shares would be construed as price manipulation under the new framework. In practice, the changes in shares outstanding that our data capture over 1930--1934 primarily reflect share retirements arising from reorganizations, mandatory sinking fund payments, and call provisions---involuntary or contractually required reductions rather than discretionary cash distributions to shareholders.

\medskip
\noindent We agree that modern readers would benefit from this context, and we have added a footnote to Section 5 clarifying the nature of ``net repurchases'' in the 1930s and noting that this component of total payout largely captures mechanical share retirements rather than deliberate equity distributions.

\medskip
\noindent This does not affect any of our substantive conclusions. As the referee notes, Table 4 shows that the payout effect is driven entirely by cash dividends (column 2 is significant), while the net repurchase coefficient (column 3) is statistically insignificant in 1933 and 1934. The channel relevant to our debt overhang interpretation---shareholders extracting value through discretionary distributions in anticipation of losing their claim on the assets---operates through dividends, not through these involuntary share retirements.
