\noindent \textit{\textcolor{red!60!black}{
First, I appreciate the improvement in measuring $d_{it}$ relative to all long-term obligations involving fixed contractual payments, but this only partly addresses my concerns. Preferred shares are not interest bearing, and thus may behave quite differently than debt during downturns or when firms are close to distress. I understand that there is nothing the author can do about this because bank debt is simply too small, but the paper should acknowledge this limitation more clearly and briefly discuss the potential confounders that cannot be addressed due to how firms structured their debt at that time.
}}

\bigskip

\noindent The referee raises a valid point that we address more explicitly in the revised manuscript. Preferred shares are not interest-bearing: their dividends are discretionary and deferring them does not trigger default. This flexibility means that preferred shares behave quite differently from fixed-income obligations in distress situations. Because preferred shares appear in the denominator of $\tilde{d}$ but not the numerator, firms with a larger preferred share component have lower measured gold exposure. The concern is that high-$\tilde{d}$ firms---which rely more heavily on inflexible bond financing---may also be more generally vulnerable to economic downturns, independently of gold clause uncertainty. In that case, the investment differential we document in 1933--1934 could partly reflect a general debt-rigidity effect rather than the specific overhang from gold clause litigation.

\medskip
\noindent We take several steps to address this concern, and we now discuss them explicitly in the manuscript. First, our preferred share placebo test (column 6 of Table 1) directly tests the alternative explanation: when we replace the numerator of $\tilde{d}$ with preferred shares (holding the denominator fixed), the 1933 and 1934 coefficients are positive and statistically insignificant. If the effect were driven by the general flexibility difference between preferred-heavy and bond-heavy firms, we would expect a negative effect here as well---firms with more preferred shares in the numerator would have lower measured exposure and thus higher investment. The absence of any effect is inconsistent with this story. Second, the temporal pattern of coefficients in Figure 3 is difficult to reconcile with a general debt-rigidity explanation: the effect of $\tilde{d}$ is concentrated precisely in 1933--1934 and reverses after the 1935 Supreme Court ruling, whereas a mechanism based on the rigidity of bond financing would predict persistent effects whenever economic conditions deteriorate (as in 1937--1938, where we observe no differential effect). Third, the industry-year fixed effects in column 1 of Table 6 absorb time-varying shocks that may differentially affect firms by industry and liability composition, and the characteristic-interaction specifications in columns 2--10 allow leverage, size, and other observables that correlate with liability structure to follow their own time paths.

\medskip
\noindent We nonetheless acknowledge that these tests do not fully eliminate the concern. An ideal research design would isolate variation in gold clause exposure while holding the debt-versus-preferred composition constant, but the institutional structure of the period---where virtually all corporate bonds had gold clauses and preferred shares had none---means this variation cannot be cleanly separated from liability composition. We have added a paragraph to the limitations discussion in Section 5 acknowledging this constraint explicitly.
