\noindent \textit{\textcolor{red!60!black}{
I appreciate using 1936--37 as a placebo. While this helps addressed concerns about downturns driving the results, there are other important macro differences between both periods---such as the collapse of bond issuance, that limited rollover---that may affect exposed firms more in 1933--34 beyond the uncertainty of the abrogation of the gold cause. That is, the placebo helps but only for a subset of the concerns about confounders. To that end, the robustness regressions are more helpful. Though the findings are broadly reassuring, they do point to either the thinness of the data or a lack of robustness. The authors cannot control for industry $\times$ year and $X_{it} \times$ year at the same time, so the fixed effects vary across specifications in Table 6. The paper argues this is done ``To assess robustness to firm-level controls separately from industry-level controls, this specification omits industry-year fixed effects.'' This sounds like a copout. Given the concerns of New Deal policies as confounders, which may have affected firms differently given their characteristics, one may want to control for both. My sense is that they lack power, as even without the industry-year FEs the significance is lost for $1934 \times d$ across several specifications for Columns 2--10. I would like to see the results with industry-year FEs for these columns as well. If significance is lost across the board, then the paper should acknowledge it and make its best case to defend their preferred specifications due to limited power---but readers should know whether the effects are sensitive so they can pass their own judgement.
}}

\bigskip

\noindent We thank the referee for these comments and address each in turn.

\medskip
\noindent \textit{Placebo and the rollover channel.} The referee correctly notes that the 1936--37 placebo addresses recession-driven confounders but not the collapse of bond issuance that may have disproportionately affected gold-exposed firms---which held more bonds---through a rollover channel. This concern is addressed directly by column 3 of Table 4, which excludes firms with bonds maturing at any point between 1931 and 1934. The 1933 and 1934 coefficients remain $-0.058$ and $-0.037$, essentially unchanged from the baseline, indicating that the investment effect is not driven by firms with immediate refinancing needs.

\medskip
\noindent \textit{Industry-year fixed effects in columns 2--10.} We agree that readers should be able to assess the sensitivity of the results to this choice directly. We have re-run columns 2--10 of Table 7 (Table 6 in the previous version of the manuscript) replacing year fixed effects with industry-year fixed effects, so that all ten columns share the same fixed-effect structure as column 1. The results are reported in Internet Appendix Table~IA.19, whose columns (1)--(9) correspond to columns 2--10 of Table 7.

\medskip
\noindent The paper's main result rests on the baseline specification of Table 4, which is already confirmed to be robust to industry-year fixed effects by column 1 of Table 7: the 1933 and 1934 coefficients are $-0.059^{***}$ and $-0.036^{**}$, nearly identical to the baseline. The specifications in columns 2--10 of Table 7 are supplementary robustness checks for observable firm heterogeneity, not the preferred specification. Among those supplementary checks, adding industry-year fixed effects leaves $\tilde{d}$ negative and significant at the 5\% level in all nine columns, and $1933 \times \tilde{d}$ significant in eight of nine.

\medskip
\noindent The referee is correct that $1934 \times \tilde{d}$ loses significance in six of nine columns when industry-year fixed effects are added. We want to be clear, however, that this is a power problem rather than a robustness failure. The point estimates for $1934 \times \tilde{d}$ are negative and consistent in magnitude across all nine specifications, ranging from $-0.011$ to $-0.036$, with no sign reversals or attenuation. It is the standard errors that widen, not the coefficients that shrink. This pattern is characteristic of reduced identifying variation, not of a coefficient that disappears under scrutiny.

\medskip
\noindent The precision loss has a mechanical explanation. For the portfolio decile specifications, the decile indicators are constructed from 1930 firm characteristics, and within a 2-digit industry firms tend to cluster in similar deciles. The decile-period dummies and industry-year fixed effects therefore absorb overlapping variation in investment, widening standard errors. For the all-controls linear specification (column 2 of Table 7, shown as column (1) of Table~IA.19), the problem is even more direct: when industry-year fixed effects are added, eight of the thirty-seven characteristic-period interactions are dropped for perfect multicollinearity---the after-period interactions are absorbed entirely by the industry-year cells---so that specification is no longer the fully-specified linear controls model. Because $1934 \times \tilde{d}$ has a smaller point estimate than $1933 \times \tilde{d}$, the same widening of standard errors is sufficient to push it below conventional thresholds while the 1933 coefficient survives.

\medskip
\noindent Column 1 of Table 7 remains our preferred specification for addressing the New Deal confounder concern. Industry-year fixed effects absorb any shock that affected an industry uniformly in a given year, which covers the canonical channels through which New Deal policies influenced investment. The characteristic controls in columns 2--10 address a distinct concern---that gold exposure may proxy for observable firm characteristics that followed differential investment trajectories---and they continue to provide reassuring evidence even when industry-year fixed effects are added, since $\tilde{d}$ remains significant throughout. We acknowledge that combining both robustness exercises simultaneously comes at a power cost, discuss this limitation explicitly in Section~5, and provide IA Table~IA.19 so that readers can form their own judgment.
