\noindent \textit{\textcolor{red!60!black}{
Additional comment (cover letter)\\
A key issue is whether the authors can clearly disentangle the effects of uncertainty about the abrogation of gold clauses from other confounders---other policies and firm characteristics, and whether it is about the gold clause vs interest-bearing leverage. There is not much they can do about the second given how firms structured their debt. I appreciate the refinement in the definition of the treatment effect, but the ideal case would be not to have preferred shares either. I am willing to look passed this, but the paper should be more upfront. The bigger issue is other confounders. They have tried to address this in the robustness section in Table 6, but as you can see they cannot control for a full set of fixed effects. What bothers me more is that they have not shown us the results with all effects, and instead state they do not include industry-year FEs in all columns to assess the robustness to industry and firm separately. This is a weak argument. If the issue is that they have too few firms to do this without the treatment effects being killed, they should say that. Readers may understand, but they need to know. And I would like to see how bad effects get---is it noisy or do the results become small and insignificant? I also find the placebo less helpful than the paper claims, but that's a personal taste.
}}

\bigskip

\noindent We are grateful for the referee's overall assessment and for the clarity of this summary. We agree with the central message---that the paper should be upfront about what the data can and cannot establish---and we have revised the manuscript accordingly. We respond to the two main issues in turn, and indicate where each is now addressed in the paper.

\medskip
\noindent \textit{Gold clause exposure versus interest-bearing leverage (preferred shares).} The referee is correct that the ideal design would isolate gold-clause exposure while holding the debt-versus-preferred composition fixed, and that the institutional structure of the period does not permit this: virtually all corporate bonds of the era carried gold clauses, while preferred shares carried none. We no longer leave this implicit. Section~5.5 now contains an explicit limitations paragraph stating that $\tilde{d}$ is necessarily entangled with the composition of a firm's fixed claims, that preferred-heavy firms may behave differently in distress for reasons unrelated to gold clauses, and that our tests mitigate but cannot fully eliminate this concern. We retain the preferred-share placebo (column~6 of Table~4), which finds no investment effect when the numerator of $\tilde{d}$ is replaced with preferred shares, as the most direct evidence that the effect is not driven by the general flexibility difference between bond-heavy and preferred-heavy firms.

\medskip
\noindent \textit{Other confounders and the full set of fixed effects.} We agree that the previous draft's justification for not always including industry-year fixed effects read as a rationalization, and we have removed that framing. We now do two things. First, we state the real reason plainly in Section~5.5: with a sample of this size, absorbing industry-year variation and characteristic-year variation simultaneously exhausts the identifying variation available to estimate the treatment effects. Second, and most importantly, we now show the results. Internet Appendix Table~IA.19 re-estimates all of columns~2--10 of Table~7 with industry-year fixed effects, so the reader sees exactly ``how bad effects get.'' The answer is that they become noisier, not small: across all nine specifications the average exposure effect $\tilde{d}$ remains negative and significant at the 5\% level, $1933\times\tilde{d}$ remains significant in eight of nine, and the $1934\times\tilde{d}$ point estimates remain negative and stable in magnitude ($-0.011$ to $-0.036$, no sign reversals) even where they lose significance. This is the signature of reduced power rather than a disappearing effect, and we now say so directly rather than asking the reader to take it on faith.

\medskip
\noindent \textit{On the placebo.} We take the referee's point that the 1936--37 placebo addresses only a subset of confounders---chiefly recession-driven ones---and not, for example, the collapse of bond issuance and the attendant rollover risk. We have tempered the paper's language about the placebo accordingly and now lean more heavily on the direct robustness checks, including the exclusion of firms with bonds maturing during the litigation window (column~3 of Table~4), which speaks specifically to the rollover channel.

\medskip
\noindent Taken together, these revisions are intended to make the paper's limitations visible to readers while preserving what we believe is the core, robust finding: gold-exposed firms reduced investment specifically during the 1933--1934 litigation window and reversed afterward, a pattern that survives industry-year fixed effects in our preferred specification and that is not reproduced by the preferred-share or bank-debt placebos.
