\noindent \textit{\textcolor{red!60!black}{
That said, I think there is one larger issue outstanding. The authors reference the portfolio returns (stock market responses) to various legal developments in section 3 (page 10). This analysis is insightful but not well-explained. In my opinion, the return analysis deserves a table and more detail on the data and summary statistics, some of which can be provided in the appendix. A figure might help too. Consider time series of (cumulative) returns for a) the market, b) firms with gold exposure (unweighted), firms with gold exposure (Weighted as indicated in footnote 10) and d) firms without gold exposure. Such a figure with ``event lines'' (joint resolution, first lawsuits, potentially lower court rulings, start of Supreme Court arguments (poor government showing), Supreme Court decision) would visualize the argument of the authors. I could also see the return analysis in a regression framework. The point here is that illustrate that market clearly responded to relevant events around the abrogation supporting the key identification argument of the authors.
}}

\bigskip

\noindent Thank you for this suggestion. We have added a table (Table~1) and three event study figures (Figures~3--5) to the paper.

\medskip
\noindent \textit{Main evidence.} The central result is Event~1: the Joint Resolution (May~26--June~6, 1933). The gold-exposure-weighted portfolio gained $+31.2\%$ over this nine-day window against a market gain of $+12.0\%$, yielding a CAPM cumulative abnormal return of $+16.1\%$. This is precisely the pattern the identification argument predicts: because the abrogation reduced the real debt burden of firms with gold-clause exposure, those firms should gain more than the market upon the resolution's passage. The $+16.1\%$ CAR isolates this differential effect by stripping out the market-wide component through a pre-abrogation beta of 0.92. Events~2 and~3 produce CARs of $-0.7\%$ and $+0.9\%$, respectively---in the right direction but modest in magnitude, and not on their own compelling. The main identification evidence rests on Event~1, corroborated by the formal regression analysis in Section~5. Table~1 reports the full results; Panel~B provides summary statistics for the daily return series over the full sample.

\medskip
\noindent \textit{Figures.} The three event study figures plot the cumulative returns for the market and the gold-exposure-weighted portfolio over a window surrounding each event, normalized to zero at the close of the last trading day before the event begins. We show these two series because the gap between the market-wide and gold-weighted returns is the quantity directly relevant to our identification argument. Following the referee's suggestion of a single time series with event lines, we have also added Figure~IA.2 in the Internet Appendix, which plots the cumulative returns of both series across the entire litigation period (March~1933--April~1935) with all key dates marked: the gold standard suspension, the Joint Resolution, the Supreme Court oral arguments, and the decision. Regarding the first lawsuits and lower court rulings suggested by the referee: the first lawsuits were filed in May~1933, concurrent with the Joint Resolution, and we are not aware of lower court rulings over this period that produced discernible market reactions.

\medskip
\noindent \textit{On the oral arguments event.} The $-0.7\%$ three-day CAR understates the full impact visible in Figure~4. Over the six trading days immediately following the arguments (January~11--17), the gold-weighted portfolio declined a further $4.6\%$ against a market decline of $3.0\%$, as news of the government's poor showing continued to filter through press coverage. By January~13, the \textit{New York Times} reported Liberty Bond prices at their highest level since 1917 \citep{NYT1935}, reflecting investor expectations that the government would lose the case. Taken together, the cumulative decline from January~7 through January~17 was $5.1\%$ for the gold-weighted portfolio and $3.9\%$ for the market.

\medskip
\noindent \textit{On the regression framework.} The regression-based identification evidence is developed formally in Section~5. The CARs in Table~1 complement that analysis by providing event-specific estimates of the gold-weighted portfolio's return in excess of its CAPM benchmark, estimated over the full pre-abrogation period.

